Hypertension and microbiome

### 2019-05-16 articletwo.Rmd
DIAB missing

```{r glm htn lacto groups}
glm.hypertension.lactogroup <- glm(HYPERTENSION ~ lacto_groups + BL_AGE + SEX,
                  family = binomial(link=logit),
                  data = df.genus.salt) %>%
    broom::tidy(conf.int = TRUE, conf.level = 0.95, exponentiate = TRUE) %>%

odds.hypertension.lactogroup <- glm.hypertension.lactogroup %>%
    filter(!grepl("Intercept", term)) %>%
    select(term, estimate, conf.low, conf.high) %>%
    add_row(term = "lacto_groups1", estimate = 1.0, conf.low = NA, conf.high = NA) %>%
    dplyr::filter(grepl("lacto", term))

glm.hypertension.lactogroup %>%
    mutate_if(is.numeric, round, 3) %>%
    kable
```

>>>>

```{r glm htn lacto groups}
glm.hypertension.lactogroup <- glm(HYPERTENSION ~ lacto_groups + BL_AGE + SEX,
                  family = binomial(link=logit),
                  data = df.genus.salt)

odds.hypertension.lactogroup <- glm.hypertension.lactogroup %>%
    broom::tidy(conf.int = TRUE, conf.level = 0.95, exponentiate = TRUE) %>%
    filter(!grepl("Intercept", term)) %>%
    select(term, estimate, conf.low, conf.high) %>%
    add_row(term = "lacto_groups1", estimate = 1.0, conf.low = NA, conf.high = NA) %>%
    dplyr::filter(grepl("lacto", term))

glm.hypertension.lactogroup %>%
    broom::tidy(conf.int = TRUE, conf.level = 0.95, exponentiate = TRUE) %>%
    mutate_if(is.numeric, round, 3) %>%
    kable
```

```{r check odds model assumptions}
g.odds.autoplot <- autoplot(glm.hypertension.lactogroup,
                            which = 1:4,
                            nrow = 1,
                            ncol = 2,
                            label.size = 3,
                            size = 0.1) +
    theme_minimal()
ggsave(file = "cache/odds-autoplot.png", plot=g.odds.autoplot, height=10, width=6, dpi = 300)
